---
title: "BA830 Team Project-Team 13"
author: "Antonio Moral Cevallos, Bosoo Kim, Jiajian(Sylar) Guo, Manushi Patel, Ying(Amber) Wu, Yixuan Wang"
date: "4/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction
(Amber)

```{r message=FALSE}
library(data.table)
library(tidyverse)
library(lfe)
library(fixest)
library(lubridate)
library(stargazer)
library(modelsummary)
library(mltools)
library(knitr)
library(broom)
library(purrr)
# load dataset
treatment <- fread('Cognitive_Test_1.csv')
control<- fread('Cognitive_Test_2.csv')
```

```{r message=FALSE, warning=FALSE}
# Data cleaning
treatment <- treatment[, treatment := 1]
control <- control[, treatment := 0]
total <- rbind(treatment, control)
total$StartDate <- as.Date(total$StartDate, format= "%Y-%m-%d")
total <- total[!(total$Finished=='False')]
total <- total[c(3:28,31:53), c("StartDate", "IPAddress", "Duration (in seconds)", "LocationLatitude", "LocationLongitude", "Q2", "Q3", "Q4", "Q5", "SC0", "treatment")]
IPadd <- split(total,total$IPAddress)
total2 <- data.frame()
for(x in IPadd){total2 <- rbind(total2,x[1,])}
total <- total2
```

```{r}
# change column names and data type
colnames(total)[c(1,3,6,7,8,9,10)] = c("date","duration","age","gender","GPA","work_experience","score")
total$duration <- as.numeric(total$duration)
total$score <- as.numeric(total$score)
total$age <- as.factor(total$age)
total$gender <- as.factor(total$gender)
total$GPA <- as.factor(total$GPA)
total$work_experience <- as.factor(total$work_experience)
```

### Method
(Manushi, Bosoo)


### Data Analysis
(Antonio, Yixuan, Bosoo)

```{r echo=FALSE, fig.height=3, fig.width=3}
##average score for treatment vs control
score_graph <- total[, .(mean_score = mean(score)), by = treatment]
score_graph$treatment <- as.factor(score_graph$treatment)
ggplot(score_graph, aes(x = treatment, y = mean_score, fill=treatment)) + geom_bar(stat = 'identity', width = 0.3) + ggtitle("Average Score")

##average completion time for treatment vs control
duration_graph <- total[, .(mean_duration = mean(duration)), by = treatment]
duration_graph$treatment <- as.factor(duration_graph$treatment)
ggplot(duration_graph, aes(x = treatment, y = mean_duration, fill=treatment)) + geom_bar(stat = 'identity', width = 0.3) + ggtitle("Average Completion time")
```

* t-test
```{r echo=TRUE}
t1 <- t.test(total[treatment == 1, score], total[treatment == 0, score])
t2 <- t.test(total[treatment == 1, duration], total[treatment == 0, duration])
tab <- map_df(list(t1, t2), tidy)
tab
```

Since p-value is larger than 0.05, the true difference in mean scores between the control group and treatment group is not statistically significant from 0. In other words, the mean scores between two groups are not significantly different. Similarly, the mean completion time between two groups are also not significantly different.


#### Randomization check

```{r include=FALSE}
treatment_g <- total[treatment==1]
treatment_g <- one_hot(treatment_g, cols = c('age','gender','GPA','work_experience'))
control_g <- total[treatment==0]
control_g <- one_hot(control_g, cols = c('age','gender','GPA','work_experience'))
#Age
age_treat <- summary(treatment_g[,c('age_<20','age_20-30','age_>30')])[4,]
age_u20_treat <- mean(treatment_g$`age_<20`)
age_2030_treat <- mean(treatment_g$`age_20-30`)
age_o30_treat <- mean(treatment_g$`age_>30`)
age_contr <- summary(control_g[,c('age_<20','age_20-30','age_>30')])[4,]
age_u20_cont <- mean(control_g$`age_<20`)
age_2030_cont <- mean(control_g$`age_20-30`)
age_o30_cont <- mean(control_g$`age_>30`)
u20_binomtest<- binom.test(sum(treatment_g$`age_<20`),length(treatment_g$`age_<20`),p = age_u20_cont )
a20to30_binomtest <- binom.test(sum(treatment_g$`age_20-30`),length(treatment_g$`age_20-30`),p = age_2030_cont )
o30_binomtest <- binom.test(sum(treatment_g$`age_>30`),length(treatment_g$`age_>30`),p =age_o30_cont )
#Gender
male_treat <- mean(treatment_g$gender_Male)
female_treat <- mean(treatment_g$gender_Female)
nonbi_treat <- mean(treatment_g$`gender_Non-binary / third gender`)
male_contr<- mean(control_g$gender_Male)
female_contr <- mean(control_g$gender_Female)
nonbi_contr <- mean(control_g$`gender_Non-binary / third gender`)
male_binomtest<- binom.test(sum(treatment_g$gender_Male),length(treatment_g$gender_Male),p = male_contr )
female_binomtest <- binom.test(sum(treatment_g$gender_Female),length(treatment_g$gender_Female),p = female_contr )
nonbi_binomtest<- binom.test(sum(treatment_g$`gender_Non-binary / third gender`),length(treatment_g$`gender_Non-binary / third gender`),p = nonbi_contr )
#GPA
gpau3_treat <- mean(treatment_g$`GPA_<3.00`)
gpau3.5_treat <- mean(treatment_g$`GPA_3.00 - 3.50`)
gpao3.5_treat <- mean(treatment_g$`GPA_>3.50`)
gpau3_contr <- mean(control_g$`GPA_<3.00`)
gpau3.5_contr <- mean(control_g$`GPA_3.00 - 3.50`)
gpao3.5_contr <- mean(control_g$`GPA_>3.50`)
gpau3_binomtest <- binom.test(sum(treatment_g$`GPA_<3.00`),length(treatment_g$`GPA_<3.00`),p = gpau3_contr )
gpau3.5_binomtest <- binom.test(sum(treatment_g$`GPA_3.00 - 3.50`),length(treatment_g$`GPA_3.00 - 3.50`),p = gpau3.5_contr )
gpao3.5_binomtest <- binom.test(sum(treatment_g$`GPA_>3.50`),length(treatment_g$`GPA_>3.50`),p = gpao3.5_contr )
#Work Experience
noyears_treat <- mean(treatment_g$`work_experience_0 years`)
u2years_treat <- mean(treatment_g$`work_experience_< 2 years`)
u5years_treat <- mean(treatment_g$`work_experience_2 - 5 years`)
u9years_treat <- mean(treatment_g$`work_experience_6 - 9 years`)
noyears_contr <- mean(control_g$`work_experience_0 years`)
u2years_contr <- mean(control_g$`work_experience_< 2 years`)
u5years_contr <- mean(control_g$`work_experience_2 - 5 years`)
u9years_contr <- mean(control_g$`work_experience_6 - 9 years`)
noyears_binomtest <- binom.test(sum(treatment_g$`work_experience_0 years`),length(treatment_g$`work_experience_0 years`),p = noyears_contr )
u2years_binomtest <- binom.test(sum(treatment_g$`work_experience_< 2 years`),length(treatment_g$`work_experience_< 2 years`),p = u2years_contr )
u5years_binomtest <- binom.test(sum(treatment_g$`work_experience_2 - 5 years`),length(treatment_g$`work_experience_2 - 5 years`),p = u5years_contr )
u9years_binomtest <- binom.test(sum(treatment_g$`work_experience_6 - 9 years`),length(treatment_g$`work_experience_6 - 9 years`),p = u9years_contr )
```

```{r echo=FALSE}
#Create a table with the data from above, make it legible and exportable.
#AGE
age <- c(c(age_u20_treat,age_2030_treat,age_o30_treat), c(age_u20_cont,age_2030_cont,age_o30_cont), c(u20_binomtest$p.value,a20to30_binomtest$p.value,o30_binomtest$p.value))
age_matrix <-  matrix(age,ncol = 3)
colnames(age_matrix) <- c('Treatment','Control','P-value')
rownames(age_matrix) <- c('Under 20','Between 20-30','Over 30')
age_table <- kable(age_matrix)
age_table

#GENDER
gender <- c(c(male_treat,female_treat,nonbi_treat), c(male_contr,female_contr,nonbi_contr), c(male_binomtest$p.value, female_binomtest$p.value, nonbi_binomtest$p.value))
gender_matrix <- matrix(gender,ncol = 3)
colnames(gender_matrix) <- c('Treatment','Control','P-value')
rownames(gender_matrix) <- c('Male','Female','NonBinary')
gender_table <- kable(gender_matrix)
gender_table

#GPA
grades <- c(c(gpau3_treat, gpau3.5_treat, gpao3.5_treat),c(gpau3_contr, gpau3.5_contr, gpao3.5_contr), c(gpau3_binomtest$p.value, gpau3.5_binomtest$p.value, gpao3.5_binomtest$p.value))
grades_matrix <- matrix(grades,ncol = 3)
colnames(grades_matrix) <- c('Treatment','Control','P-value')
rownames(grades_matrix) <- c('Under 3.0', 'Between 3.0-3.5','Over 3.5')
grades_table <- kable(grades_matrix)
grades_table

#EXPERIENCE
experience <- c(c(noyears_treat, u2years_treat, u5years_treat, u9years_treat), c(noyears_contr, u2years_contr, u5years_contr, u9years_contr), c(noyears_binomtest$p.value, u2years_binomtest$p.value, u5years_binomtest$p.value,  u9years_binomtest$p.value))
experience_matrix <- matrix(experience, ncol = 3)
colnames(experience_matrix) <- c('Treatment','Control','P-value')
rownames(experience_matrix) <- c('No Experience','Under 2 years','Between 2-5','Between 6-9+')
experience_table <- kable(experience_matrix)
experience_table
```


#### Regression of Score on treatment

```{r}
score_reg <- lm(score~treatment, data=total)
score_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Age
```{r}
score_age_reg <- feols(score~treatment + age, data=total, se='white')
score_age_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Gender
```{r}
score_gender_reg <- feols(score~treatment + gender, data=total, se='white')
score_gender_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for GPA
```{r}
score_gpa_reg <- feols(score~treatment + GPA, data=total, se='white')
score_gpa_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Work Experience
```{r}
score_exp_reg <- feols(score~treatment + work_experience, data=total, se='white')
score_exp_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for All covariates
```{r message=FALSE, warning=FALSE}
score_all_reg <- feols(score~treatment + age + gender + GPA + work_experience, data=total, se='white')
score_all_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```


#### Regression of completion time on treatment
```{r}
duration_reg <- feols(duration~treatment, data=total, se='white')
duration_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Age
```{r}
duration_age_reg <- feols(duration~treatment + age, data=total, se='white')
duration_age_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Gender
```{r}
duration_gender_reg <- feols(duration~treatment + gender, data=total, se='white')
duration_gender_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for GPA
```{r}
duration_gpa_reg <- feols(duration~treatment + GPA, data=total, se='white')
duration_gpa_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for Work Experience
```{r}
duration_exp_reg <- feols(duration~treatment + work_experience, data=total, se='white')
duration_exp_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```

* Controlling for All covariates
```{r message=FALSE, warning=FALSE}
duration_all_reg <- feols(duration~treatment + age + gender + GPA + work_experience, data=total, se='white')
duration_all_reg %>% tidy() %>% kable(col.names = c("Predictor", "Coefficient", "SE", "T-Stat", "P-Value"), digits = c(0, 3, 3, 3, 3), align = 'c')
```


### Limitations
(Sylar)


### Conclusion
(Antonio)



