---
title: "BA830_Final_Project"
author: "Ying Wu (U30529371)"
date: "27/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(tidyverse)
library(lfe)
library(fixest)
library(lubridate)
library(stargazer)
library(modelsummary)
library(mltools)
library(knitr)
library(ggplot2)
```

##data loading 
```{r}
treatment <- fread('Cognitive_Test_1.csv')
control<- fread('Cognitive_Test_2.csv')
```

##data cleaning 
```{r}
treatment <- treatment[, treatment := 1]
control <- control[, treatment := 0]
total <- rbind(treatment, control)
total$StartDate <- as.Date(total$StartDate, format= "%Y-%m-%d")
total <- total[!(total$Finished=='False')]
total <- total[c(3:28,31:53), c("StartDate", "IPAddress", "Duration (in seconds)", "LocationLatitude", "LocationLongitude", "Q2", "Q3", "Q4", "Q5", "SC0", "treatment")]
# select the first one record of each IPAddress
IPadd <- split(total,total$IPAddress)
total2 <- data.frame()
for(x in IPadd){
  total2 <- rbind(total2,x[1,])
}
total <- total2
# change column names
colnames(total)[1] = "date"
colnames(total)[3] = "duration"
colnames(total)[6] = "age"
colnames(total)[7] = "gender"
colnames(total)[8] = "GPA"
colnames(total)[9] = "work_experience"
colnames(total)[10] = "score"
# change data type
total$duration <- as.numeric(total$duration)
total$score <- as.numeric(total$score)
total$age <- as.factor(total$age)
total$gender <- as.factor(total$gender)
total$GPA <- as.factor(total$GPA)
total$work_experience <- as.factor(total$work_experience)
```

##average score for treatment vs control
```{r}
treatment_avg <- total[total$treatment == 1, mean(score)]
treatment_avg

control_avg <- total[total$treatment == 0, mean(score)]
control_avg
```
We found that average score of control group is slightly higher than that of treatment group. 

```{r}
this_graph <- total[, .(mean_score = mean(score)), by = treatment]
this_graph$treatment <- as.factor(this_graph$treatment)
ggplot(this_graph, aes(x = treatment, y = mean_score, fill=treatment)) + geom_bar(stat = 'identity') + ggtitle("Average Score per Treatment & Control")
```

```{r}
that_graph <- total[, .(Time_in_seconds = mean(duration)), by = treatment]
that_graph$treatment <- as.factor(that_graph$treatment)
ggplot(that_graph, aes(x = treatment, y = Time_in_seconds, fill=treatment)) + geom_bar(stat = 'identity') + ggtitle("Time taken of Treatment & Control")
```

##ttest
```{r}
t.test(total[treatment == 1, score], 
       total[treatment == 0, score])
```
Since p-value is larger than 0.05, the true difference in mean scores between the control group and treatment group is not statistically significant from 0. In other words, the mean scores between two groups are not significantly different. 